\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.6in, top=0.55in, bottom=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{colorlinks=true, urlcolor=blue!70!black, linkcolor=blue!70!black}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\pagenumbering{gobble}
\setlist{nosep, leftmargin=1.5em, topsep=3pt, itemsep=2pt}

% Custom commands for consistent formatting
\newcommand{\projectentry}[5]{%
    \noindent\textbf{#1} \hfill #2 \\[2pt]
    #4 \hfill {\small #3} \\[1pt]
    #5\par\vspace{8pt}%
}

\newcommand{\projectentrysingle}[3]{%
    \noindent\textbf{#1} \hfill #2 \\[2pt]
    #3\par\vspace{8pt}%
}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries Jie Xin} \\[8pt]
    [\href{mailto:cs.xinjie@gmail.com}{email}] \quad
    [\href{https://github.com/ftxj}{github}] \quad
    [\href{https://ftxj.github.io}{homepage}]
\end{center}

\vspace{2pt}

% Experience
\section{Experience}

\noindent\textbf{NVIDIA} \hfill Shanghai, China \\
\textit{Senior Compute Architect} \hfill 2022 -- Present
\begin{itemize}
    \item Researching automated end-to-end model performance optimization on next-gen GPUs (Hopper, Blackwell, Rubin)
    \item Developed deep learning compilers (CuTile, Triton-to-CuTile) and MLPerf benchmark optimization
    \item Collaborating with PyG, Megatron-LM, and OpenAI Triton teams on compiler infrastructure
\end{itemize}

\vspace{4pt}

% Education
\section{Education}

\noindent\textbf{Huazhong University of Science and Technology} \hfill Wuhan, China \\
\textit{M.S. in Computer Science} \hfill 2019 -- 2022

\vspace{6pt}

\noindent\textbf{Huazhong University of Science and Technology} \hfill Wuhan, China \\
\textit{B.S. in Computer Science} \hfill 2015 -- 2019

\vspace{4pt}

% Projects
\section{Projects}

\projectentrysingle{Agent for Compiler}{2026 -- Present}
{Designing a lightweight harness system specifically for compiler optimization.}

\projectentry{Triton-to-CuTile}{2024 -- 2025}{[\href{https://github.com/triton-lang/Triton-to-tile-IR}{code}]}
{OpenAI incubation project; compiler bridge connecting Triton frontend to CuTile backend.}
{Enabling Triton users to target NVIDIA's optimized tile programming infrastructure.}

\projectentry{CuTile}{2023 -- Present}{[\href{https://github.com/NVIDIA/cutile-python}{code}] [\href{https://developer.nvidia.com/blog/tag/cutile/}{blog}]}
{CUDA Tile programming standard for NVIDIA GPUs.}
{Designed and implemented optimization passes for deep learning workloads.}

\projectentry{NvFuser}{2022 -- 2023}{[\href{https://github.com/csarofeen/pytorch/commits/devel/?author=ftxj}{code}] [\href{https://pytorch.org/blog/introducing-nvfuser-a-deep-learning-compiler-for-pytorch/}{blog}]}
{PyTorch JIT compiler achieving 1.2x--2.5x speedup on GNN models.}
{Enabled gather/scatter/index\_select graph operations for sparse workloads.}

\projectentry{OpenFold2 Training}{2023 -- 2023}{[\href{https://github.com/mlcommons/hpc_results_v3.0/tree/main/NVIDIA/benchmarks/openfold}{code}] [\href{https://arxiv.org/abs/2404.11068}{paper}] [\href{https://developer.nvidia.com/blog/optimizing-openfold-training-for-drug-discovery/}{blog}]}
{MLPerf HPC v3.1 \#1 submission with 7.5x e2e speedup.}
{Optimized protein structure prediction training on large-scale GPU clusters.}

\projectentry{GPT-3 Training}{2023 -- 2023}{[\href{https://github.com/NVIDIA/Megatron-LM}{code}]}
{MLPerf Training v4.0; contributed 1.02x training speedup on 175B model.}
{Optimized distributed training pipeline for large language models.}

\projectentry{PyTorch Geometric TorchScript}{2022 -- 2022}{[\href{https://github.com/pyg-team/pytorch_geometric/commits/master/?author=ftxj}{code}]}
{Added TorchScript support for PyG community, enabling JIT compilation for GNN models.}
{Contributed core infrastructure for production deployment of graph neural networks.}

\projectentry{SpMM on GPU -- Champion, MIT/IEEE Graph Challenge}{2021 -- 2021}{[\href{https://github.com/CGCL-codes/Graphchallenge21}{code}] [\href{https://ieeexplore.ieee.org/document/9622791}{paper}]}
{High-performance sparse matrix multiplication; up to 652x speedup over cuSPARSE.}
{Won 1st place in the 2021 MIT/IEEE/Amazon Graph Challenge competition.}

\vspace{4pt}

% Current Focus
\section{Current Focus}

\noindent My research interest has fully shifted to AI agents -- exploring how LLMs can autonomously optimize compilers, automate performance tuning, and transform traditional software development workflows.

\end{document}
